Rotations and Insecticide Resistance the story

### 2019-02-26 inst/documents/rotations_notes.Rmd
starting to get mortality in plots
insecticide change using mortality now working - but may not for diff insecticides

@@

@@

# todo: we want to look at changing insecticides according to mortality rather than resistance frequency

@@

~ maybe come back to i_in_use ribbons not meeting issue
~ rename rot_criterion to rot_threshold
~ add in some unit-tests ?
~ check how gens_under_thresh are counted in sensi_an_rotations1
    summarise(gens_dep_under50 = sum(resistance < 0.5 &
                                     #finds insecticide in use = this one
                                     resist_gene==paste0('insecticide',insecticide), na.rm=TRUE)) %>%
                                 summarise(tot_gens_dep_under50 = sum(gens_dep_under50)) %>%    
                                 unlist()

>>>>

# 21/2/2019

Cool getting there with mortality checking :
Best to set logy to F to be able to see 90% mort

dfr <- run_rot(start_freqs = 0.0001, eff=1, logy=FALSE)

# 26/2/2019

starting to get mortality switch working.

seems OK from messages but plots don't look right

in the plots looks like still responding to frequency rather than mortality ??

Something a bit weird going on ...
Currently the threshold mortality is not reached in the plots, but seems that frequency is.

Fixed!!! mostly a problem that eff,dom_sel,rr was not passed to new calc functions (and I didn't notice because they had defaults).

dfr <- run_rot(start_freqs = 0.000000001, eff=1, logy=FALSE, mort_or_freq='mort', rot_interval=0, threshold=0.9)

@@

~ fix that mortality calc in plots and that for switching is currently repeated
~ check it works with diff insecticides i.e. eff=c(0.7,0.8,0.9) I suspect not because mort_from_resist() or something else not properly vectorised.

whatever I do I need to make mort/survival thing more transparent

options
~ pass as mortality and then convert to survival for calculation
~ pass as survival convert to mortality for plot

~ change origin of git repo in RStudio, probably need to do from git

@@

@@

~ maybe come back to i_in_use ribbons not meeting issue
~ add in some unit-tests ?
~ check how gens_under_thresh are counted in sensi_an_rotations1
    summarise(gens_dep_under50 = sum(resistance < 0.5 &
                                     #finds insecticide in use = this one
                                     resist_gene==paste0('insecticide',insecticide), na.rm=TRUE)) %>%
                                 summarise(tot_gens_dep_under50 = sum(gens_dep_under50)) %>%    
                                 unlist()

### 2019-02-26 inst/documents/rotations_story.Rmd
insecticide change using mortality now working - but may not for diff insecticides

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0.005, coverage=1, migration = 0, dom_cos = 0, rot_criterion = 0.9, start_freqs = 0.001)

@@

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0.005, coverage=1, migration = 0, dom_cos = 0, rot_criterion = 0.9, start_freqs = 0.001)

@@

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0.005, coverage=1, migration = 0, dom_cos = 1, rot_criterion = 0.9, start_freqs = 0.001)

@@

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0.005, coverage=1, migration = 0, dom_cos = 1, rot_criterion = 0.9, start_freqs = 0.001)

>>>>

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0.005, coverage=1, migration = 0, dom_cos = 0, threshold = 0.9, start_freqs = 0.001)

@@

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0.005, coverage=1, migration = 0, dom_cos = 0, threshold = 0.9, start_freqs = 0.001)

@@

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0.005, coverage=1, migration = 0, dom_cos = 1, threshold = 0.9, start_freqs = 0.001)

@@

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0.005, coverage=1, migration = 0, dom_cos = 1, threshold = 0.9, start_freqs = 0.001)
